\documentclass{tccv}
\usepackage[english]{babel}
\usepackage {bookmark}
\pdfinfo{
   /Author (Jong Park)
   /Title  (Curriculum Vitae / Resume for Jong Park)
   /CreationDate (2019-09-13)
   /Subject (PDFLaTeX)
   /Keywords (PDF;LaTeX)
}
\begin{document}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%           Personal Info           %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\part{Jong J. Park}
\personal
	[github.com/parkj6]
	{LinkedIn.com/in/JongJPark/}
	% {5356 SW Olivia Pl. \newline 
	{Beaverton, OR 97007}
	{808-346-4924}
	{JongJPark.jobs@gmail.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%             Education              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
	\begin{yearlist}
		\item{2011}
			{Kauai Community College}
			{Associate Degree in Liberal Arts}
		\item {2019}
			{Oregon State University}
			{Bachelor of Science in Computer Science}
	\end{yearlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%             Language               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section {Communication Skills}
	\begin{factlist}
		\item {English}{Proficient}
		\item {Korean}{Native Speaker}
		\item {Japanese}{Basic}
		\item {American Sign Language}{Basic}
	\end{factlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%          Actual Skill Set          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software Skills}
	\begin{factlist}
		\item {Android}
			{Android Debugging Bridge (ADB),
			Software Development Kit(SDK)}
		\item {Assembly}
			{NASM (x86), ARM, AVR}
		\item {Version Control}
			{Git, GIthub, SVN}
		\item{Framework}
			{Maven (MVC Framework), \\
			 Ninja, Handlebar}
		\item{Container}
			{Docker,
			Virtualization}
		\item{Imperative}
			{C/++, Java}
		\item{Scripting}
			{Python,
			 Bash (-nix),
			 Batch(DOS/Windows), 
			 Makefile}
		\item{Web}
			{HTML, CSS, Javascript, MySQL}
		\item{Database}
			{SQL}
		\item{Functional}
			{Haskell}
		\item{Logical}
			{Prolog}
		\item{Parsing}
			{(f)lex, Bison(yacc)}
		% \item{Computation Diagram}
		% 	{State Diagram, }
		\item{Data Analysis}
			{Matlab, R (R-Studio), Excel}
		\item{Network}
			{WireShark}
		\item{Multimedia}
			{GIMP (Images) \\
			Audacity (Audio)\\
			Open Shot (Video)} 
		\item{Documentation}
			{\LaTeX, Markdown}
	\end{factlist}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		 Related School Work 	%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Schoolwork}
	\begin{yearlist}
		% \item[optional: what has been achieved]{years}{subject}{notes}
		\item [Recreated the game 'Aces Up' with team of three.]
			{} %{CS 361}
			{Software Engineering I }
			{MVC, Git, Teamwork, Java, Ninja, Maven}

		\item [Made a simple website where users and draw or browse the previous drawing]
			{} %{CS 290}
			{Web Development}
			{HTML, Node.JS, Handlebar, CSS, Javascript}

		\item {} %{CS 340}
			{Introduction to Databases}
			{MySQL, Flask, Node.JS, Relational Algebra }

		\item [Created a simple app called 'Study Buddy', a simple chatroom to test asyncronous communication] 
			{} %{CS 496}
			{Mobile and Cloud Development}
			{Android Development, Java, Firebase, AWS}

		\item {} %{MTH 351}
			{Numerical Analysis}
			{Matlab, Data Analysis}

		\item {} %{ST 314}
			{Statistics for Engineers}
			{R, Excel}
		
		\item []{} %{CS 312}
			{System Administration}
			{Virtualization, Docker, Alpine, DNS \& DHCP deployment, Network Design, Firewalls, Router \& WAP deployment, Virtual Private Networks, Windows Server, Active Directory, Dev Ops, Configureation Management, Automation, Ansible, Server Storage (RAID configurations), Scheduled Tasks}

		\end{yearlist}
	
\section{Other Schoolwork}
	\begin{yearlist}
		\item {} %{CS 381}
			{Programming Language Fundamentals}
			{Haskell, Prolog}

		\item {} %{CS 480}
			{Translators}
			{(f)lex, bison(yacc)}

		\item [Senior Design] {} %{Capstone}
			{Capstone Project: \href{http://web.engr.oregonstate.edu/~parkj6/capstone/final_poster.pdf} {Avalanche Detection Through Deep Learning}}
			{Machine Learning, Python, Keras, Theano (Tensorflow), /LaTeX, Markdown}

		\item {} %{CS 271}
			{Computer Architecture and Assembly Language}
			{Assembly in x86 Architecture (NASM)}

		\item {} %{CS 352}
			{Usability Enginieering}
			{UI/UX, Prototyping, myBalsamiq}

		\item {} %{ECE 271}
			{Digital Logic Design}
			{Logic Gates, data types and representation, boolean algebra, state machines}
			
		\item [As well as Linux User Group] {} %{CS 344, 444}
			{Operating Systems I, II}
			{Linux, bash, ssh, c, c++}

	\end{yearlist}



\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%	  If Resume, Comment this section   %%
%% 	     Other Work Experience         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Retail Work Experience}
	 \begin{eventlist}
		 \item {Jun 2018 -- Sep 2018}
			 {\textbf{Shigezo Izakaya}	Portland, OR}
			 {Sushi Chef}

			 Creating items in the menu with customization catered to customer's tastes. 
			 Engaging with customers who sat in front of the sushi bar for customer service and quality management. 

		\item {Oct 2017 -- Jun 2018}
			{\textbf{Sugoi Sushi}	Corvallis, OR}
			{Sushi Chef}

			Preparing menu items and/or customer's special request items quickly and efficiently while ensuring that there are at least 70\% of the belt is filled with edible dishes.
			
		\item {Aug 2013 -- Dec 2015}
			{\textbf{American Eagle Outfitters}	Tigard, OR}
			{Lead Cashier /\\ Assistant to Operations Manager}
			
			As a Jean Expert, gave critique and recommendation to customers on their outfit search. The attention to detail and excellent customer service led me to an employee of the month.\\
			As a Lead Cashier, trained new employees with POS register systems, authorized employee-transactions, returns, and no-item sale transactions. Also was tasked with administrating the monthly Lost Prevention Test and Safety Guideline to employees.\\
			As an Assistant to the Operations Manager, configured all new technologies, troubleshoot all electronics when needed, and ensured all employees had a proper working headsets for clear line of communications. 
			All while having a constant communication between coworkers, customers and management to ensure exemplary customer service. 

		\item {Feb 2014 -- Dec 2015 }
			{\textbf{I Love Sushi}	Beaverton, OR}
			{Server /\\ Assistant to Manager}

			Train other servers how to user POS system. 
			Hosting and general server duties 
			(Answering phones for takeouts, 
			guiding the customer on different menu items,
			serving drinks (alcoholic and non-alcoholic),
			replacing fountain soda/kegs,
			restocking dishes and cups,
			janitorial servives at the end of the day).

		
		\item {May 2006 - Jun 2013}
			{\textbf{Korean BBQ Restaurant}	Kapaa, HI}
			{Manager}
			
			Overseeing all the hired servers.
			Translating between Owner and cooks in the kitchen when neccesary.
			General server duties 
			(Answering phones for takeouts,
			explaining the menu and sometimes translating the menu for international customers,
			sering dishes,
			dishwashing,
			janitorial and general upkeep).
			Sometimes only server managing and balancing work in the restaurant. 
			Server logging: Balancing the money at the end of the day.

	\end{eventlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		 Teaching Experience         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching Experience}
	 \begin{eventlist}
		 \item {Aug 2008 -- Mar 2011}
			 {\textbf{Kauai Community College}           Lihue, HI}
			 {Peer Tutor, In-class tutor}

			\textbf{Logic}: Introductory course in logical reasoning \\
			\textbf{Math}: Basic elementary to college level Physics with Calculus \\
			In-class teacher assistant for:\\
			 \begin{factlist}
				 \item{ICS 100}
					 {Introduction to Information \& Computer Science}
				 \item{ICS 111}
					 {Introduction to Computer Programming/Java}
				 \item{Phil 100}
					 {Introduction to Logic}
				 \item{Phy 271,272}
					 {College Physics with Calculus}
			 \end{factlist}
			 Normally, each tutors are tasked with a single students at a time, I was given a special exception to tutor up to 4 students at 3 different level of math. I was recommended by teachers and was given a pay-raise the same year. 


		\item {Aug 2006 -- Mar 2011}
			{\textbf{Kumon Math and Reading Center}       Eleele, HI}
			{Tutor}

			Chaperoning kids under 18 until picked up by a family member or a responsible party.
			Administrating exams, guiding young mind to learn how to learn and promote growth of their skill set. 
			Responsible for opening and closing the center. 
				
	\end{eventlist}


		
		
\end{document}